---
title: "Your title here"
author:
  - Author First
  - Author Second
format: docx
---

```{r}
#| label: setup
#| echo: false
#| message: false

# Load packages
library(tidyverse)
```

```{r}
#| label: load-data
#| echo: false
#| message: false

# Load the data: choose your dataset (delete the code for the other datasets)
# Check the README link for more information about the dataset

# - Verified Oldest People
# README: https://github.com/rfordatascience/tidytuesday/blob/master/data/2023/2023-05-30/readme.md#verified-oldest-people
oldest_people <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-05-30/centenarians.csv")

# - Chocolate
# README: https://github.com/rfordatascience/tidytuesday/tree/master/data/2022/2022-01-18#chocolate-ratings
chocolate <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/chocolate.csv")

# - Olympics
# README: https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-07-27/readme.md#the-olympics
olympics <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-07-27/olympics.csv')

# - Transit cost
# README: https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-01-05/readme.md#transit-costs-project
transit_cost <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-01-05/transit_cost.csv')

# - Student to teacher ratio
# README: https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-05-07#global-student-to-teacher-ratios
student_ratio <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-07/student_teacher_ratio.csv")

```

## Introduction

- What is this data set about?

- What questions could be answered with the dataset?

## About the data

- What are the variables in the dataset?

## Data visualization

- Please make at least one data visualization

- You may make more if it helps you explain something interesting about the data

## Discussion

- What is the **message** in your data visualization?

- What is particularly interesting about this dataset?
