---
title: "Your title here"
author:
  - Author First
  - Author Second
format: docx
---

```{r}
#| label: setup
#| echo: false
#| message: false

# Load packages
library(tidyverse)
```

```{r}
#| label: load-data
#| echo: false
#| message: false

# Load the data: choose your dataset (delete the code for the other datasets)
# Check the README link for more information about the dataset

# - World's Oldest People
# README: https://github.com/rfordatascience/tidytuesday/blob/master/data/2023/2023-05-30/readme.md#verified-oldest-people
oldest_people <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-05-30/centenarians.csv")

# - Olympics
# README: https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-07-27/readme.md#the-olympics
olympics <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-07-27/olympics.csv')

# - Chocolate ratings
# README: https://github.com/rfordatascience/tidytuesday/tree/master/data/2022/2022-01-18#chocolate-ratings
chocolate <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/chocolate.csv")

# - Transit cost
# README: https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-01-05/readme.md#transit-costs-project
transit_cost <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-01-05/transit_cost.csv')

# - Student to teacher ratios
# README: https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-05-07#global-student-to-teacher-ratios
student_ratio <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-07/student_teacher_ratio.csv")
```

## Introduction

- What is the dataset **about**?

- Where does the dataset **come from**?

- What **question(s)** will you answer by analyzing the dataset?

## Data visualization

- Please generate **at least two graphs** that show relationships between variables in the data

## Discussion

- What is the **message** in your data visualization?

- What **insights** can the dataset provide (in other words, **what conclusions** can you draw from the data)?

## References

- List any references that you cite here. You may use any reference style, as long as you are consistent.